Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (2).} Let $h', h^*$, and $\bm{t}$ be as defined in statement (2). Let us represent $h'$ as $[x_1,x_2] \times y$. Accordingly, $h^*$ can be written as $[x_1, \minleft(h')] \times y$. Additionally, let $x$ be the x-coordinate of the vertical segment $\bm{t}[k-1]$. The effective horizontal segment of $\bm{t}$ can be represented as $[x_1,x] \times y$.

@@

We will first prove $\contained_{R_{k-2}}(\bm{t})\subseteq \cross_{R_{k-2}}(h^*)$. For this purpose, we will show that any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$ also covers $h^*$. It suffices to show that $h^*$ is contained in the effective horizontal segment of $\bm{t}$. Combining the definition of $\minleft(h')$ (see \eqref{eqn:minleft}), and the fact that $x$ is the x-coordinate of $\bm{t}[k-1]$, we have $\minleft(h') \le x$. This implies that $h^* = [x_1, \minleft(h')] \times y$ is contained in $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$.

@@

Next, assuming that the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ are sorted in descending order of $\xright(r)$, we will prove that $\contained_{R_{k-2}}(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:

@@

\minipg{0.8\linewidth} {
    If a rectangle $r \in \contained_{R_{k-2}}(h^*)$ satisfies the condition that $\xright(r) \ge$ the x-coordinate of $\bm{t}[k-1]$, then $r$ must be in $\contained_{R_{k-2}}(\bm{t})$.
}

@@

\noindent To prove the above, we must explain why $r$ contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, we know that $r$ covers the segment $[x_1, \minleft(h')] \times y$. Therefore, $[x_1, \minleft(h')] \subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$.
As $\xright(r) \ge x$ (recall that $x$ is the x-coordinate of $\bm{t}[k-1]$), we have $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. This means that $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$.

>>>>

\extraspacing \underline{\em Proof of Statement (2).} Let $h', h^*$, and $\bm{t}$ be as defined in statement (2). Let us represent $h'$ as $[x_1,x_2] \times y$; accordingly, $h^*$ can be written as $[x_1, \minleft(h')] \times y$. Additionally, let $x$ be the x-coordinate of the vertical segment $\bm{t}[k-1]$. The effective horizontal segment of $\bm{t}$ can then be represented as $[x_1,x] \times y$.

@@

Firstly, we will prove $\contained_{R_{k-2}}(\bm{t})\subseteq \cross_{R_{k-2}}(h^*)$. For this purpose, we will show that any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$ also covers $h^*$. It suffices to show that $h^*$ is contained in the effective horizontal segment of $\bm{t}$. Combining the definition of $\minleft(h')$ (see \eqref{eqn:minleft}), and the fact that $x$ is the x-coordinate of $\bm{t}[k-1]$, we have $\minleft(h') \le x$. This implies that $h^* = [x_1, \minleft(h')] \times y$ is contained in $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$.

@@

Secondly, assuming that the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ have been sorted in descending order of $\xright(r)$, we will prove that $\contained_{R_{k-2}}(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:

@@

\minipg{0.8\linewidth} {
    If a rectangle $r \in \contained_{R_{k-2}}(h^*)$ satisfies the condition that $\xright(r) \ge x$ (where as defined before $x$ is the x-coordinate of $\bm{t}[k-1]$), then $r$ must be in $\contained_{R_{k-2}}(\bm{t})$.
}

@@

\noindent To prove the above, we must explain why $r$ contains the effective horizontal segment of $\bm{t}$. Since $r \in \contained_{R_{k-2}}(h^*)$, we know that $r$ covers the segment $[x_1, \minleft(h')] \times y$. Therefore, $[x_1, \minleft(h')] \subseteq [\xleft(r), \xright(r)]$ and $y \in [\ybot(r), \ytop(r)]$.
Using also the given condition $\xright(r) \ge x$, we can derive $[x_1, x] \subseteq [\xleft(r), \xright(r)]$. This means that $[x_1, x] \times y$, i.e. the effective horizontal segment of $\bm{t}$, is contained in $r$.
